Naturalness in U(1) extensions of the MSSM

### 2015-01-21 paper/e6ssm-tuning-paper.tex
Commented out the placeholder abstract so that we don't forget to write a proper one

\begin{abstract}
% Copied SUSY2014 abstract as placeholder
With the discovery of a 125 GeV Standard Model (SM) like Higgs boson
and rising lower bounds on the masses of superpartners, minimal models
of low energy supersymmetry (SUSY) appear to be increasingly fine
tuned. In the Minimal Supersymmetric Standard Model (MSSM) large stop
masses, needed to obtain the observed Higgs mass, give a significant
contribution to fine tuning. $U(1)$ extensions of the MSSM that solve
the $\mu$-problem have new F- and D-term contributions to the Higgs
mass, allowing a 125 GeV Higgs with lighter stops and so alleviating
the associated fine tuning. However, it was recently demonstrated,
within a constrained version of the Exceptional Supersymmetric
Standard Model (E$_6$SSM) defined at the Grand Unification (GUT)
scale, that the presence of a massive $Z'$ boson introduces a
substantial new source of tuning in these theories at tree level. Here
we consider the impact of this tuning when we remove the fine tuning
that depends on assumptions about the SUSY breaking scale, by setting
the SUSY breaking parameters at low energies. We find that the
existing experimental bounds on the $Z'$ mass impose an effective
lower bound on the fine tuning, which does not depend on assumptions
about SUSY breaking.  We compare our results against the tuning in the
MSSM with the SUSY breaking terms also defined at low energies.

>>>>

\begin{abstract}
The abstract.
% Copied SUSY2014 abstract as placeholder
% With the discovery of a 125 GeV Standard Model (SM) like Higgs boson
% and rising lower bounds on the masses of superpartners, minimal models
% of low energy supersymmetry (SUSY) appear to be increasingly fine
% tuned. In the Minimal Supersymmetric Standard Model (MSSM) large stop
% masses, needed to obtain the observed Higgs mass, give a significant
% contribution to fine tuning. $U(1)$ extensions of the MSSM that solve
% the $\mu$-problem have new F- and D-term contributions to the Higgs
% mass, allowing a 125 GeV Higgs with lighter stops and so alleviating
% the associated fine tuning. However, it was recently demonstrated,
% within a constrained version of the Exceptional Supersymmetric
% Standard Model (E$_6$SSM) defined at the Grand Unification (GUT)
% scale, that the presence of a massive $Z'$ boson introduces a
% substantial new source of tuning in these theories at tree level. Here
% we consider the impact of this tuning when we remove the fine tuning
% that depends on assumptions about the SUSY breaking scale, by setting
% the SUSY breaking parameters at low energies. We find that the
% existing experimental bounds on the $Z'$ mass impose an effective
% lower bound on the fine tuning, which does not depend on assumptions
% about SUSY breaking.  We compare our results against the tuning in the
% MSSM with the SUSY breaking terms also defined at low energies.
